Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-05-10 ms.qmd
Found out the match problem Climate data reversed Lat and long. Checking with Alex about if this affects the data or just a quick renaming

# Create a match column.
climate2 <- climate %>% mutate(match = interaction(Species, Latitude, Longitude)) %>% dplyr::select(Species, Latitude, Longitude, match, cv, sd, mean, acf_lag1, acf_all)

>>>>

# Create a match column.
climate2 <- climate %>% mutate(match = interaction(Species, Longitude, Latitude)) %>% dplyr::select(Species, Latitude, Longitude, match, cv, sd, mean, acf_lag1, acf_all)
